---
title: "Homework - features and elements of multiple regression"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

```{r}
library(tidyverse)
library(GGally)
library(ggplot2)
library(fastDummies)
library(ggfortify)
library(mosaic)

```


# MVP

1. Load the `diamonds.csv` data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant [Kaggle page](https://www.kaggle.com/shivam2503/diamonds/)

<br>
```{r}
diamonds <- read_csv("data/diamonds.csv")

diamonds

summary(diamonds)

```

2. We expect the `carat` of the diamonds to be strong correlated with the physical dimensions `x`, `y` and `z`. Use `ggpairs()` to investigate correlations between these four variables.

<br>

```{r}

ggpairs(diamonds, progress = FALSE)

```


3. So, we do find significant correlations. Let's drop columns `x`, `y` and `z` from the dataset, in preparation to use only `carat` going forward.

<br>
```{r}

diamonds <- diamonds %>% 
  select(-x,-y,-z)

```


4. We are interested in developing a regression model for the `price` of a diamond in terms of the possible predictor variables in the dataset. 

  i. Use `ggpairs()` to investigate correlations between `price` and the predictors (this may take a while to run, don't worry, make coffee or something).

  ii. Perform further `ggplot` visualisations of any significant correlations you find.
  
<br>

```{r}

diamonds

ggpairs(diamonds, progress = FALSE)

diamonds %>% 
  ggplot() +
  aes(x = price, y = carat) +
  geom_point() 

diamonds %>% 
  ggplot() +
  aes(x = price, y = cut) +
  geom_point()
  
diamonds %>% 
  ggplot() +
  aes(x = price, y = color) +
  geom_point()
  
diamonds %>% 
  ggplot() +
  aes(x = price, y = clarity) +
  geom_point()
  
diamonds %>% 
  ggplot() +
  aes(x = price, y = depth) +
  geom_point()

diamonds %>% 
  ggplot() +
  aes(x = price, y = table) +
  geom_point()

```


5. Shortly we may try a regression fit using one or more of the categorical predictors `cut`, `clarity` and `color`, so let's investigate these predictors: 

  i. Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

  ii. Use the `dummy_cols()` function in the `fastDummies` package to generate dummies for these predictors and check the number of dummies in each case.

i) Required dummy variables for:
      Cut        = 4 (5-1)
      Clarity    = 7 (8-1)
      Color      = 6 (7-1)
      
```{r}

diamonds_dummy_cut <- diamonds %>%
  fastDummies::dummy_cols(select_columns = "cut", remove_first_dummy = TRUE, remove_selected_columns = TRUE)

diamonds_dummy_clarity <- diamonds %>%
  fastDummies::dummy_cols(select_columns = "clarity", remove_first_dummy = TRUE, remove_selected_columns = TRUE) 

diamonds_dummy_color <- diamonds %>%
  fastDummies::dummy_cols(select_columns = "color", remove_first_dummy = TRUE, remove_selected_columns = TRUE)

diamonds_dummy_cut
diamonds_dummy_clarity
diamonds_dummy_color

```
    
    
6. Start with simple linear regression. Regress `price` on `carat` and check the regression diagnostics.

<br>
Looks like carat has a influence on the price of the diamond

```{r}

model <- lm(price ~ carat, data = diamonds)

autoplot(model)

summary(model)

plotModel(model)

```



7. Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.


    
<hr>

Looks like the colour of the diamond has a significat influence on the price.
```{r}

model <- lm(price ~ carat + color, data = diamonds)

autoplot(model)

summary(model)

plotModel(model)

```


# Extension
    
8. Try adding an interaction between `log(carat)` and your chosen categorical predictor. Do you think this interaction term is statistically justified?

<br>

9. Find and plot an appropriate visualisation to show the effect of this interaction
    