---
title: "Clustering homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


* You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings. 

* We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers. 

* Perform k-means clustering and chose a value of k.

* Visualise the clustering for your chosen value of k.

* Do you think the clustering seems a good fit for this data?

* Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the 'Segmentation & clustering intro' lesson). 


```{r}

library(tidyverse)
library(CodeClanData)
library(broom)
library(janitor)
library(factoextra)

```

```{r}

#Loading and cleaning data

customer <- read_csv("data/mall_customers.csv")

customer

customer <- customer %>%
  clean_names() %>% 
  select(customer_id, annual_income_k, spending_score_1_100)

customer

```

```{r}

# Creating a scale

customer_scale <- customer %>% 
  mutate(across(c(annual_income_k,spending_score_1_100), scale))

customer_scale

customer_scale %>%
  as_tibble() %>%
  pivot_longer(cols = c(annual_income_k,spending_score_1_100), names_to = "type", values_to = "value") %>% 
  group_by(type) %>%
  summarise(mean = round(mean(value)), sd = sd(value))

```

```{r}

# Checking the number of clusters required


fviz_nbclust(customer_scale, kmeans, method = "wss", nstart = 25)

fviz_nbclust(customer_scale, kmeans, method = "silhouette", nstart = 25)

fviz_nbclust(customer_scale, kmeans, method = "gap_stat")


# 3 clusters looks optimal, mainly looking from the elbow plot

```

```{r}

cluster_customer_scale <- kmeans(customer_scale, 3, nstart = 25)

cluster_customer_scale

cluster <- augment(cluster_customer_scale, customer)

cluster

```

```{r}
cluster %>% 
  ggplot() +
  aes(annual_income_k, spending_score_1_100, colour = .cluster) +
  geom_point() 


cluster %>% 
  group_by(.cluster) %>%
  summarise(mean(annual_income_k), mean(spending_score_1_100)) 


# Looking at the data you can break it down into 3 groups. Low, medium and high income groups/clusters. There may be a case to break it down even further into 5 clusters as the data seems to have a certain shape to it. 

```

