--- title: "`dplyr` Weekend Homework" output: html_document: toc: true
toc_float: true df_print: paged css: ../../../styles.css pdf_document: default
---
```{r setup, include=FALSE} knitr::opts_chunk$set(echo = TRUE, eval = TRUE) ```
<br>
As this is your first weekend homework, here are some tips:
* Try to schedule some time in your weekend to work on the homework so it's not
suddenly Monday morning and you haven't gotten started yet (it happens). *
Remember that the weekend homework is for your learning, so try to use it as an
opportunity to apply and consolidate everything you've learned in the week. *
Also use it as an opportunity to spend a bit more time making your code readable
and reproducible, by practising commenting and writing some text around your
steps and findings. You will thank yourself later! * This will be especially
useful for this specific weekend homework as it's very open-ended and you will
eventually forget your own thought process * A bit obvious, but don't spend your
entire weekend working on the homework! Remember to spend time doing things you
enjoy and rest up ahead of the following week.
The data for this weekend homework is scraped from Goodreads (a website all
about books) and made publicly available on Kaggle. You can read more about the
data [here](https://www.kaggle.com/jealousleopard/goodreadsbooks).
# MVP
### First steps
Load necessary packages and read in `books.csv`. Investigate dimensions,
variables, missing values - you know the drill!

```{r}
library(tidyverse)
library(janitor)
library(stringi)

```

```{r}
# Loading the data set and having a first look at it

books <- read_csv("data/books.csv")
dim(books)  
glimpse(books)
str(books)


head(books, 10)
tail(books, 10)

sum(is.na(books))
nrow(books)
nrow(drop_na(books))

# Does not make sence as nrow(drop_na(books)) = 8469 (so that means in 8469 rows there is an na value)
#view(books)
#nrow(books)
    

```
```{r}
# Deleted the troubling row

books <- books[1:8471,]

tail(books, 5)

```

```{r}
# 1st delete and combine some of the columns to work with smaller data

books <- books %>% 
  mutate(total_review_count = text_reviews_count + ratings_count) %>% 
  select(authors, 
         title, 
         language_code, 
         num_pages, 
         average_rating, 
         total_review_count, 
         publication_date, 
         publisher
         )

```

```{r}
# 2nd see if there are any missing values (only 2 rows so we will delete them), non-english values

sum(is.na(books))

books <- drop_na(books)
# if_else function?
# stri_enc_isascii(books)
  
# sum(is.na(books))

```
(1) Wanted to find the most common Language (needed to clean the language section a little)


```{r}
#glimpse(books)
# distinct(books, authors)
# distinct(books, language_code)

books %>%
  select(language_code) %>%
  mutate(language = case_when(language_code == "en-US" ~ "eng",
                              language_code == "en-GB" ~ "eng", 
                              language_code == "en-CA" ~ "eng",
                              TRUE                     ~ language_code)
         ) %>% 
  group_by(language) %>% 
  summarise(number_of_books_in = n()) %>% 
  arrange(desc(number_of_books))
  
# why does count not work?
#summarise(book_language = count(title))
```
(2) Wanted to find the most popular publisher that a writer would want to publish with in general.

```{r}

books %>% 
  group_by(publisher) %>% 
  summarise(number_of_books_published = n()) %>% 
  arrange(desc(number_of_books_published ))

# Found that there are a number of similar publishing companies, So will have to figure a way how to clean them as they are not all written in the same way and doing it individualy would be too long.
```
(3) Wanted to find the longest book.

```{r}

#glimpse(books)
books %>% 
  select(authors, title, num_pages) %>% 
  arrange(desc(num_pages))

```
(4) Wanted to find the most popular book.

```{r}
# used the total_review_count column that I created, assuming the most reviewed book would be the most popular one. 

books %>% 
  select(authors, title, total_review_count) %>% 
  arrange(desc(total_review_count))

```
Wanted to find the Oldest book in this record.


```{r}
books %>% 
  select(authors, title, publication_date) %>% 
  arrange(publication_date)

```



### Up to you
Now it's up to you... For this weekend homework there will be no specific tasks,
just you and this dataset! Using everything you've learned this week, try to
describe/summarise at least 5 things about this dataset - using R and the
tidyverse of course! Feel free to find and use new functions if there is
something that the tidyverse doesn't offer, but do try to use this homework to
apply what you have learned this week. Be prepared to share one of your findings
on Monday!
### Remember
Before you submit, go through your weekend homework and make sure your code is
following best practices as laid out in the `coding_best_practice` lesson.